Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-03-12 draft.tex
polish abstract

\begin{abstract}
  Our goal is to obtain a complete set of angular observables
  arising in a generic multi-body process without the need to carry
  out a likelihood fit of the angular distribution to the measured
  events. Instead, we apply the method of moments that relies
  both on the orthogonality of angular functions and the estimation of
  integrals by Monte Carlo techniques. The main advantage of
  this method is that the joint distribution of all observables
  given the data can be easily extracted, even for very few
  events. Our main contribution is to show explicitly how systematic
  uncertainties from detector-resolution and acceptance effects can
  be incorporated into a general algorithm. Finally, we present the
  necessary process-dependent formulae needed for direct
  implementation of the method for several rare decays of
  interest.
\end{abstract}

>>>>

\begin{abstract}
  Our goal is to obtain a complete set of angular observables arising
  in a generic multi-body process. We show how this can be achieved
  without the need to carry out a likelihood fit of the angular
  distribution to the measured events. Instead, we apply the method of
  moments that relies both on the orthogonality of angular functions
  and the estimation of integrals by Monte Carlo techniques. The big
  advantage of this method is that the joint distribution of \emph{all}
  observables can be easily extracted, even for very few events. The
  method of moments is shown to be robust against mismodeling of the
  angular distribution. Our main result is an explicit algorithm that
  accounts for systematic uncertainties from detector-resolution and
  acceptance effects. Finally, we present the necessary
  process-dependent formulae needed for direct application of the
  method to several rare decays of interest.
\end{abstract}
